PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-21 qfenv_paper/qf_environment.tex
Major changes to QF section

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. By analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the redshift evolution of the quiescent fraction for a complete mass range in our environments. Through this comparison we reveal the subtle effects of environment in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms that operate on the scale of our environment measure, such as strangulation and ram-pressure stripping (CITECITE).

@@

In both panels, $f_{\rm{Q}}$ increases monotonically as a function of mass for all redshift bins. This result is strongly consistent with the well established trend that generally more massive galaxies are more likely to be quenched. Furthermore, the results are also consistent with previous measurements of the quiescent fraction. Using a group-finding algorithm on the SDSS DR7 catalog, \cite{Tinker:2011aa} presented the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. Likewise at higher redshifts, our high and low environment $f_{\rm{Q}}$ results are in general agreement with the $F_{\rm{blue}}$ values for group and isolated galaxies from the zCOSMOS Redshift Survey, as presented in \cite{Iovino:2010aa}.

Though our $f_{\rm{Q}}$ results do not extend beyond masses lower than $10^{9.5} \mathcal{M}_{\odot}$, if we loosely extrapolate the monotonic relation between $f_{\rm{Q}}$ and stellar mass for the low density environment SDSS sample to lower masses, $f_{\rm{Q}}$ extends to $0$ for $\mathcal{M}_{*} < 10^{9.0} \mathcal{M}_{\odot}$. This is broadly consistent with the stellar mass threshold ($10^9 \mathcal{M}_{\odot}$) for quenching of field galaxies presented by \cite{Geha:2012aa}.

In addition to its relation with mass, in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases as redshift decreases for all masses and environments. Though restricted by the stellar mass limits, the $f_{\rm{Q}}$ evolution exhibits a slight mass dependence. $f_{\rm{Q}}$ in low density environments shows a greater evolution between redshift bins at high masses than at low masses. In contrast, the $f_{\rm{Q}}$ in high density environments shows a greater evolution between redshift bins at low masses than at high masses.

@@

% SDSS QF matches with SDSS QF of Tinker et al. 2010 who uses a group catalog. The PRIMUS QF values match reasonably well with zCOSMOS 10k in Iovino et al. 2010 and zCOSMOS 20k in Kovac et al. 2014, once disparities between color classification and SFR classifications are taken into account.

% The mass dependence of each subsample QF: reflects the color-mass relation and the morphology-mass relation
% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors. 
% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
% The redshift evolution of the QF in each 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.

While Figure \ref{fig:qf} show the apparent trends, quantitative comparisons of $f_{\rm{Q}}$ for different density environment over redshift is made challenging by the distinct stellar mass limits at each redshift bin. In order to quantify the quiescent fraction over the stellar mass complete rate, we fit each $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass, 
\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts and using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$ does not notably alter the results. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments. For both density environments, $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases similar to the trend we noted qualitatively. In addition, throughout the redshift range, high density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ is significantly greater than the low density environment $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$. However when we compute $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{high}} - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})_{\rm{low}}$, we find the difference remains constant throughout the redshift range ($ < 0.15$ throughout redshift range). Furthermore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.

>>>>

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.

@@

Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass regardless of redshift bin or environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{Blanton:2009aa}).

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly support the observed decline of global star-formation in the universe (\cite{hopkins06a}).

Also, by comparing the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time. This corresponds to the well-known mass-downsizing pattern (\cite{bundy06a}). Furthermore, the mass-downsizing trend observed in each of our environment subsample is generally consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}).

We compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ or $f_{\rm{red}}$ measurements for analogous environment classifications in literature. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. At higher mass ranges, our $f_{\rm{Q}}$ results for low and high density environments are consistent with \cite{Baldry:2006aa} $f_{\rm{red}}$ values for lowest and highest environment density, which they measure using projected neighbor density.

At higher redshifts, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which roughly covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and environment determined using a group catalog, 3D local density contrast, and overdensity respectively, compare $f_{\rm{red}}$ for different environments.

The $f_{\rm{blue}}$ values for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $f_{\rm{Q}}$ values in high and low density environments. Similarly, the $f_{\rm{red}}$ values for high and low overdensities from \cite{Kovac:2014aa} disagree with our $f_{\rm{Q}}$ values in high and low density environments.

Also, the zCOSMOS results, which are mostly consistent with each other, indicate that the $f_{\rm{red}}$ values in high density environments are greater than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. 
Furthermore, \cite{Iovino:2010aa} in their analysis finds clear mass dependence in the $f_{\rm{red}}$ evolution where $f_{\rm{red}}$ evolves by a greater amount for lower mass galaxies in both group and isolated galaxies.

 %explain the zCOSMOS results briefly. Mention the general discrepancies while highlighting the large statistics offered by PRIMUS
%If we impose the f_Q vs f_red discrepancies plotting in Kovac et al. 2014, can we explain the discrepancies between Iovino et al. 2010 and PRIMUS? Is Iovino et al. 2010 and Kovac et al. 2014 consistent with one another? 
%Note the clear mass dependence in essentially all the zCOSMOS results 
%color-density relation?

In contrast to the zCOSMOS results, for each panels in Figure \ref{fig:qf}, qualitatively, we see little mass dependence on the $f_{\rm{Q}}$ evolution. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, we require a more quantitative comparison of the $f_{\rm{Q}}$ redshift evolution. Consequently, we fit each subsample $f_{\rm{Q}}$ to a power-law parameterization as a function of stellar mass,

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.

\begin{equation} 
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from a general shift in all $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values by roughly $\sim 0.2$, we observe the same evolutionary trends.

From Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments. Remarkably, the total evolution of $f_{\rm{Q}}$ remains constant for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.

%Discuss how this is not due to contamination by environment classifications.

In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.

%PRIMUS results are roughly in agreement with zCOSMOS 10k (Iovino et al. 2010) and zCOMOS 20k (Kovac et al. 2014) once the difference between f_red and f_Q are taken into account. Discuss some general specific values. 
% Previous results, primarily from zCOSMOS 10k and 20k, have found a significant mass dependence in the f_{Q} evolution with f_{Q} increasing significantly more over redshift at lower masses. At higher masses these results find little evolution in f_Q. Though our f_{Q} values are in good agreement with these results, for the mass ranges probed in our analysis, we find little mass dependence in the f_Q evolution.

@@

% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors. 
% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
% The redshift evolution of the QF in each
